Pushdown Control-Flow Analysis via Refunctionalization

### 2018-02-15 paper.tex
misc

  In this paper, we show their correspondence and a series of transformations from a small-step 
  abstracting abstract machine to a big-step abstracting definitional interpreter. 
  The transformations include fusing, disentangling, 
  refunctionalizing and then monadification/un-CPS, each of them properly handle the collecting semantics and 
  the non-determinism of abstract interpretation. 
  The transformations also uncover several intermediary forms of abstract interpreter.
  Remarkably, we reveal how computatble precise call/return match in control-flow analysis is obtained by 
  refunctionalizing a small-step abstracting abstract machine with unbounded stack, 
  as well as explain how it been lost by defunctionalizing the higher-order continuations into 
  an algebraic data type.

@@

  \item We present an abstract interpreter written in CPS obtained from refunctionalization of small-step AAM. This abstract interpreter naturally has pushdown control-flow property, and we analyze how precise call/return match is obtained by representing evaluation context as a continuation function, as well as how it is lost by representing continuation as a data type in the defining language.

@@

In this section, we first describe the syntax of A-Normal Form (ANF) $\lambda$-calculus and a CESK machine for executing it concretely. Then we review several recent works in control flow analysis: 1) Abstracting Abstract Machine as an abstract counterpart of CESK machine, 2) abstract interpreter written in a monadically-parameterized style, and 3) precise call/return match problem and its solutions.

>>>>

  % Mention Danvy's work
  In this paper, we show their correspondence and a series of transformations from a small-step 
  abstracting abstract machine to a big-step abstracting definitional interpreter. 
  The transformations include fusing, disentangling, 
  refunctionalizing and then monadification/un-CPS, each of them properly handle the collecting semantics and 
  the non-determinism of abstract interpretation. 
  The transformations also uncover several intermediary forms of abstract interpreter.
  Remarkably, we reveal how computatble precise call/return match in control-flow analysis is obtained by 
  refunctionalizing a small-step abstracting abstract machine with unbounded stack, 
  as well as explain how it been lost by defunctionalizing the higher-order continuations into 
  an algebraic data type.

@@

  \item We present an abstract interpreter written in CPS obtained from refunctionalization of small-step AAM. This abstract interpreter naturally has pushdown control-flow property, and we show how precise call/return match is obtained by representing evaluation context as a continuation function, as well as how it is lost by representing continuation as a data type in the defining language. We also analyze its termination, soundness and complexity property.

@@

In this section, we first describe the syntax of A-Normal Form (ANF) $\lambda$-calculus and a CESK machine for executing it concretely. Then we review several recent works in control flow analysis: 1) Abstracting Abstract Machine as an abstract counterpart of CESK machine, 2) abstract interpreter written in a monadically-parameterized style, and 3) precise call/return match problem and existing solutions.
